---
title: "Capstone"
author: "David Granadier"
date: "12/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#library(limma)
#library(Glimma)
#library(edgeR)
devtools::install_github("jimhester/fstrings")
dir <- "/Users/dgranadi/Desktop/tfcb_2020/"

```

```{r}

df<- read_csv("Testing.csv")
#df 
df_mean<-select(df, -pad) %>%
  group_by(clin_diag) %>%
  summarize_all(.funs = c(mean = "mean")) %>%
  print()



```


```{r}
#Hepatocellular-Intrahepatic_cholangiocarcinoma <- df("Hepatocellular carcinoma" - "Intrahepatic cholangiocarcinoma")
df_only3<-df_mean %>%
  slice(3 , 5 , 6) %>%
  print()
 
```



```{r}

DPA_vs_HC <- (df_only3[1, -1] / df_only3[2, -1]) %>%
  print()
marker_DPA_vs_HC <- DPA_vs_HC[max.col(DPA_vs_HC)]
print(marker_DPA_vs_HC)


```

###The marker most overexpressed in Ductal Pancreatic Adenocarcinoma relative to Hepatocellular Carcinoma is ca125 and it is expressed 7.94 times higher

```{r}
#Using the inverse of the DPA vs HC dataframe, find the marker most overexpressed in HC relative to DPA
HC_vs_DPA <- (DPA_vs_HC ^-1 ) %>%
  print()
marker_HC_vs_DPA <- HC_vs_DPA[max.col(HC_vs_DPA)]
print(marker_HC_vs_DPA)
```

###The marker most overexpressed in Hepatocellular Carcinoma relative to Ductal Pancreatic Adenocarcinoma is cd56 and it is expressed 3.83 times higher


```{r}
DPA_vs_IC <- (df_only3[1, -1] / df_only3[3, -1]) %>%
  print()
marker_DPA_vs_IC <- DPA_vs_IC[max.col(DPA_vs_IC)]
print(marker_DPA_vs_IC)

```

###The marker most overexpressed in Ductal Pancreatic Adenocarcinoma relative to Intrahepatic Cholangiocarcinoma is muc2 and it is expressed 4.06 times higher

```{r}
#Using the inverse of the DPA vs IC dataframe, find the marker most overexpressed in IC relative to DPA
IC_vs_DPA <- (DPA_vs_IC ^-1 ) %>%
  print()
marker_IC_vs_DPA <- IC_vs_DPA[max.col(IC_vs_DPA)]
print(marker_IC_vs_DPA)
```

###The marker most overexpressed in Intrahepatic Cholangiocarcinoma relative to Ductal Pancreatic Adenocarcinoma is cd56 and it is expressed 10.4 times higher


```{r}
IC_vs_HC <- (df_only3[3, -1] / df_only3[2, -1]) %>%
  print()
marker_IC_vs_HC <- IC_vs_HC[max.col(IC_vs_HC)]
print(marker_IC_vs_HC)
```

###The marker most overexpressed in Intrahepatic Cholangiocarcinoma relative to Hepatic Carcinoma is ck7 and it is expressed 7.73 times higher


```{r}
#Using the inverse of the DPA vs IC dataframe, find the marker most overexpressed in IC relative to DPA
HC_vs_IC <- (IC_vs_HC ^-1 ) %>%
  print()
marker_HC_vs_IC <- HC_vs_IC[max.col(HC_vs_IC)]
print(marker_HC_vs_IC)
```

###The marker most overexpressed in Hepatic Carcinoma relative to Intragepatic Cholangiocarcinoma is cd10 and it is expressed 1.42 times higher
